Detailed Chemical Abundances with \tc

### 2015-09-01 article/ms.tex
Formatting

% Convenient colloquiualisms.
\newcommand\article{\textit Article}
\newcommand\tc{\textit{The Cannon}}

@@

\begin{abstract}
More than 15 million spectra are expected to be acquired by stellar surveys in
the coming decade. The detailed chemical abundance analysis of these data poses
a significant computational challenge. \tc provides a purely data-driven
approach to stellar parameter (label) determination. Cross-validation tests
demonstrate that the precision achievable is comparable to existing methods that
rely on model atmospheres and spectral synthesis, but \tc is $\sim300,000\times$ faster, making it perfectly apt for surveys. Simply extending the label vector
dimensionality of \tc to include individual abundances can create enormous
model difficulties, severely limiting the interpretability of the results. Here
we describe an alternative approach to including individual element abundances
in \tc. Using modest simplifications of the physics of spectral line formation,
we demonstrate precisely \textit{why} an approach like \tc works so effectively,
and provide a physically-motivated model that describes flux values, given the
stellar parameters. The inclusion of individual chemical abundances does not
impact on model flexibility, allowing for simultaneous training on detailed
chemical abundances, as well as arbitrary labels where the impact on the spectra
is unknown or poorly understood (e.g., mass, age). Crucially, we provide a link
between data-driven models and parallel works on model atmospheres and spectral
line formation, allowing for data to inform models. We demonstrate that
detailed chemical abundances can be measured with a precision of 0.0X-0.0Y~dex
in Z APOGEE spectra on a modern CPU in just one minute.
\end{abstract}

>>>>

% Convenient colloquiualisms.
\newcommand\article{\textit Article}
\newcommand\tc{\textit{The Cannon} }

@@

\begin{abstract}
More than 15 million spectra are expected to be acquired by stellar surveys in
the coming decade. The detailed chemical abundance analysis of these data poses
a significant computational challenge. \tc provides a purely data-driven
approach to stellar parameter (label) determination. Cross-validation tests
demonstrate that the precision achievable is comparable to existing methods that
rely on model atmospheres and spectral synthesis, but \tc is $\sim$300,000 times
faster, making it perfectly apt for surveys. Simply extending the label vector
dimensionality of \tc to include individual abundances can create enormous
model difficulties, severely limiting the interpretability of the results. Here
we describe an alternative approach to including individual element abundances
in \tc. Using modest simplifications of the physics of spectral line formation,
we demonstrate precisely \textit{why} an approach like \tc works so effectively,
and provide a physically-motivated model that describes flux values, given the
stellar parameters. The inclusion of individual chemical abundances does not
impact on model flexibility, allowing for simultaneous training on detailed
chemical abundances, as well as arbitrary labels where the impact on the spectra
is unknown or poorly understood (e.g., mass, age). Crucially, we provide a link
between data-driven models and parallel works on model atmospheres and spectral
line formation, allowing for data to inform models. We demonstrate that
detailed chemical abundances can be measured with a precision of 0.0X-0.0Y~dex
in Z APOGEE spectra on a modern CPU in just one minute.
\end{abstract}
